Iterative Monomorphisation

### 2024-02-14 iterative_monomorphisation.tex
continued working on introduction

\cite{mono-trans}
\cite{expr-poly-types}
\cite{sb-phd}

@@

@@

These iterations are required to generate all

After a set number of iterations, the new type arguments are used to instantiate type variables, generating new monomorphic clauses.

@@

This approach sacrifices completeness for the sake of performance. The loss of completeness occurs at the conceptual level due to the finite number of iterations. It also occurs on the practical level, due to the explosive nature of the procedure, various bounds limit the number of generated clauses.
% target page number: 0.5-1.5
\section{Background}

>>>>

%\cite{mono-trans}
%\cite{expr-poly-types}
%\cite{sb-phd}

@@

\smallskip

[sumarry of results]

@@

\smallskip

These iterations are required in order to account for inductively defined types. Consider the type constructor \verb|list| which takes a type argument, if we obtain \verb|list(alpha)| where \verb|alpha| is a type variable, it may be possible to generate the types \verb|list(int)|, \verb|list(list(int))|, ... However because new types are obtained through matching, \verb|list(list(int))| can only be obtained once \verb|list(int)| has already been added to the set of monomorphic types. This example also makes it clear that the set of types that can be generated is infinite, this explains why the number of iterations is bounded.

\smallskip

After a set number of iterations, the new type arguments are used to instantiate the type variables in the problem's clauses, generating new monomorphic clauses.

@@

This approach sacrifices completeness for the sake of performance. The loss of completeness occurs at the level of the algorithm; a finite number of iterations and at the implementation level; the explosive nature of the procedures requires various bounds which limit the number of type arguments and clauses that are generated.

% target page number: 0.5-1.5
\section{Background}
